site_map

### 2020-04-20 site_map.Rmd
update

site_list_sub_map <- site_list_sub %>% 
  select(site,lat,lon)

@@

site_map <- ggplot(data = south_africa_coast, aes(x = lon, y = lat)) + 
  #geom_raster(data = OISST, aes(x = lon, y = lat, fill = temp)) +
   geom_polygon(data = south_africa_coast, aes(x = lon, y = lat, group = group),
                fill = "grey", colour = "grey", size = 0.1, show.legend = FALSE) +
  geom_point(data = site_list_sub, aes(x = lon, y = lat), alpha = 0.8, size = 2) +
  geom_point(data = site_pixels, aes(x = lon, y = lat), colour = "black", shape = 0, alpha = 0.8, size = 2.1) +
  geom_label_repel(data =site_list_sub, aes(x = lon, y = lat, label = site), 
                     size = 4, box.padding = 2, nudge_x = 0.7, nudge_y = 0.2, 
                     segment.alpha = 0.4, force = 0.1) +
  coord_equal(xlim = c(15, 21.5), ylim = c(-35,-27), expand = 0) +
  # geom_rect(data = bbox, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
  #           alpha = 0.4, colour = "red", size = 0.1, linetype = 1) +
  # scale_x_continuous(limits = sa_lons, expand = c(0, 0), breaks = seq(15, 35, 5)) +
  # scale_y_continuous(limits = sa_lats, expand = c(0, 0), breaks = seq(-35, -30, 5)) +
  # scale_fill_viridis(
  #   option = "magma",
  #   name = "Temperature (°C)",
  #   alpha = 0.8) +
  xlab("") + ylab("") +
  # annotate("text", label = "INDIAN\nOCEAN", x = 32.00, y = -35.0,
  #            size = 4, angle = 0, colour = "black") +
    annotate("text", label = "ATLANTIC\nOCEAN", x = 16, y = -31.5,
             size =5, angle = 0, colour = "black") +
    # annotate("text", label = "Benguela", x = 15, y = -30,
    #          size = 5, angle = 302, colour = "black") +
    # annotate("text", label = "Agulhas", x = 31.7, y = -31.7,
    #          size = 5, angle = 50, colour = "black") +
  guides(fill = guide_colourbar()) +
  scale_x_continuous(expand = c(0, 0),
                       labels = scales::unit_format(unit = "°E", sep = "")) +
    scale_y_continuous(expand = c(0, 0),
                       labels = scales::unit_format(unit = "°S", sep = "")) +
  coord_fixed(ratio = 1, xlim = c(10.5, 39.5), ylim = c(-39.5, -25.5),
                expand = TRUE) +
  theme(axis.text = element_text(size = rel(1.2), colour = "black"),
        axis.text.x = element_text(vjust = 1),
        axis.text.y = element_text(hjust = 1),
        axis.title.x = element_text(vjust = 0),
        axis.title.y = element_text(angle = 90, vjust = 0.3),
        axis.ticks = element_line(colour = "black"),
        axis.ticks.length = unit(0.15, "cm"),
        panel.background = element_rect(fill = "white", colour = "black", size = 0.5),
        #panel.border = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=2),
        #(colour =" black"),
        panel.grid.major.x = element_blank(),
        #panel.grid.major.y = element_line(linetype = "dotted", size = 0.2, colour = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor = element_blank(),
        #panel.margin = unit(0.25, "lines"),
        strip.text = element_text(size = rel(1.0)),
        strip.background = element_rect(fill = "white", colour = NA),
        strip.text.x = element_text(),
        strip.text.y = element_text(angle = -90),        
        plot.background = element_rect(colour = "white"),
        plot.title = element_text(size = rel(1.2), vjust = 1),
        plot.margin = unit(c(1, 1, 0.5, 0.5), "lines"))

site_map

# pdf("Figures/site_map.pdf", width = 10, height = 7, pointsize = 4) # Set PDF dimensions
# 
# 
# africa_map <- ggplot(africa_coast, aes(x = lon, y = lat)) + 
#   theme_bw() + 
#   coord_equal() + 
#   geom_polygon(aes(group = group), colour = "black", fill = "grey80") + 
#   geom_polygon(data = sa_provinces_new, (aes(group = group))) +
#   annotate("text", label = "Africa", x = 16.0, y = 15.0, size = 3) + 
#   theme(panel.border = element_rect(colour = "black", size = 0.4), 
#         plot.background = element_blank(), 
#         axis.ticks = element_blank(), 
#         axis.text = element_blank(), 
#         axis.title = element_blank(), 
#         panel.grid.major = element_blank(), 
#         panel.grid.minor = element_blank()) +
#   coord_map(xlim = c(-20, 53), ylim = c(-36, 38), projection = "mercator") 
# africa_map
# 
# # More mapping - http://r-nold.blogspot.com/2014/06/creating-inset-map-with-ggplot2.html
# 
# vp1 <- viewport(x = 0.70, y = 0.58, w = 0.25, h = 0.25) # Africa
# vp2 <- viewport(x = 1.0, y = 1.0, w = 1.00, h = 1.00, just = c("right", "top"))  # South Africa
# print(site_map, vp = vp2)
# print(africa_map, vp = vp1)
# dev.off()
# pdf("Figures/map_fixed.pdf", width = 10, height = 7, pointsize = 4) # Set PDF dimensions
```

>>>>

site_list_sub_map <- site_list_sub %>%
  dplyr::select(site,lat,lon)

@@

site_map <- ggplot(data = south_africa_coast, aes(x = lon, y = lat)) + 
   geom_polygon(aes(group = group),fill = "grey", colour = "grey", size = 0.1, show.legend = FALSE) +
  geom_point(data = site_list_sub, aes(x = lon, y = lat), alpha = 0.8, size = 2) +
  geom_point(data = site_pixels, aes(x = lon, y = lat), colour = "black", shape = 0, alpha = 0.8, size = 2.1) +
  geom_label_repel(data =site_list_sub, aes(x = lon, y = lat, label = site), 
                     size = 4, box.padding = 2, nudge_x = 0.7, nudge_y = 0.2, 
                     segment.alpha = 0.4, force = 0.1) +
  xlab("") + ylab("") +
    annotate("text", label = "ATLANTIC\nOCEAN", x = 16, y = -31.5,
             size =5, angle = 0, colour = "black") +
  guides(fill = guide_colourbar()) +
  scale_x_continuous(expand = c(0, 0),
                       labels = scales::unit_format(unit = "°E", sep = "")) +
    scale_y_continuous(expand = c(0, 0),
                       labels = scales::unit_format(unit = "°S", sep = "")) +
  coord_fixed(ratio = 1, xlim = c(15.5, 20), ylim = c(-35,-28),
                expand = TRUE) +
  theme(axis.text = element_text(size = rel(1.2), colour = "black"),
        axis.text.x = element_text(vjust = 1),
        axis.text.y = element_text(hjust = 1),
        axis.title.x = element_text(vjust = 0),
        axis.title.y = element_text(angle = 90, vjust = 0.3),
        axis.ticks = element_line(colour = "black"),
        axis.ticks.length = unit(0.15, "cm"),
        axis.ticks.margin = unit(0.1, "cm"),
        panel.background = element_rect(fill = "white", colour = "black", size = 0.5),
        #panel.border = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=2),
        #(colour =" black"),
        panel.grid.major.x = element_blank(),
        #panel.grid.major.y = element_line(linetype = "dotted", size = 0.2, colour = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor = element_blank(),
        #panel.margin = unit(0.25, "lines"),
        strip.text = element_text(size = rel(1.0)),
        strip.background = element_rect(fill = "white", colour = NA),
        strip.text.x = element_text(),
        strip.text.y = element_text(angle = -90),        
        plot.background = element_rect(colour = "white"),
        plot.title = element_text(size = rel(1.2), vjust = 1),
        plot.margin = unit(c(1, 1, 0.5, 0.5), "lines"))

site_map 
```
